\begin{thebibliography}{KEY99}
\bibitem[CIF+99]{CIF+99}
Crosignani, A, P Invernizzi, R Ferrari, A Manzin, S Bruno, M Zuin, FB Bianchi and M Podda.
\newblock Exacerbation of chronic hepatitis D during interferon alpha administration..
\newblock {\em Ital J Gastroenterol Hepatol}, 31(1):66-9, 1999.
\newblock 
\bibitem[FBC+92]{FBC+92}
Fusconi, M, H Baum, A Caselli, F Cassani, G Ballardini, M Lenzi, U Volta, D Zauli and FB Bianchi.
\newblock Demonstration of peptide-specific and cross-reactive epitopes in proteins reacting with antimitochondrial antibodies of primary biliary cirrhosis..
\newblock {\em J Hepatol}, 15(1-2):162-9, 1992.
\newblock 
\bibitem[Gob]{Gob}
Gobry, Fr\'ed\'eric.
\newblock cECI est un T\AA{}ST\'EO\'eO G\"unther.
\newblock 
\bibitem[KMH+99]{KMH+99}
Kerkar, N, Y Ma, M Hussain, L Muratori, C Targett, R Williams, FB Bianchi, G Mieli-Vergani and D Vergani.
\newblock A novel assay for detecting antibodies to cytochrome P4502D6, the molecular target of liver kidney microsomal antibody type 1..
\newblock {\em J Immunol Methods}, 223(2):227-35, 1999.
\newblock 
\bibitem[LBS+99]{LBS+99}
Lenzi, M, S Bellentani, G Saccoccio, P Muratori, F Masutti, L Muratori, F Cassani, FB Bianchi and C Tiribelli.
\newblock Prevalence of non-organ-specific autoantibodies and chronic liver disease in the general population: a nested case-control study of the Dionysos cohort [see comments].
\newblock {\em Gut}, 45(3):435-41, 1999.
\newblock 
\bibitem[MCM+98]{MCM+98}
Muratori, L, M Cataleta, P Muratori, M Lenzi and FB Bianchi.
\newblock Liver/kidney microsomal antibody type 1 and liver cytosol antibody type 1 concentrations in type 2 autoimmune hepatitis..
\newblock {\em Gut}, 42(5):721-6, 1998.
\newblock 
\bibitem[VDF+98a]{VDF+98}
Volta, U, L De Franceschi, F Lari, N Molinaro, M Zoli and FB Bianchi.
\newblock Coeliac disease hidden by cryptogenic hypertransaminasaemia..
\newblock {\em Lancet}, 352(9121):26-9, 1998.
\newblock 
\bibitem[VDF+98b]{VDF+98b}
Volta, U, L De Franceschi, N Molinaro, F Cassani, L Muratori, M Lenzi, FB Bianchi and AJ Czaja.
\newblock Frequency and significance of anti-gliadin and anti-endomysial antibodies in autoimmune hepatitis..
\newblock {\em Dig Dis Sci}, 43(10):2190-5, 1998.
\newblock 
\bibitem[ZCB99]{ZCB99}
Zauli, D, F Cassani and FB Bianchi.
\newblock Auto-antibodies in hepatitis C..
\newblock {\em Biomed Pharmacother}, 53(5-6):234-41, 1999.
\newblock 
\end{thebibliography}
