\cleardoublepage
  \setcounter{secnumdepth}{-1}
  \section{To Do List}
\label{sec:todo}



\todoprio{For the next release}

\subsection{The Graphical User Interface}
\label{todo:next:gui}


  \begin{itemize}
  \item \Active Refactoring the \filenm{Gnome/Index.py} code. \assign{ptr}
    \begin{itemize}
    \item Documenting the new \textsc{api}.
    \item Providing for multiple index views; switching them.
    \item \Think Better data structures for widget interface -- but see
      also future gtktreeview \& associates.
    
    \end{itemize}
  \item \Done Incremental updates. \assign{ptr}

  \item \Done Combined author/title field in Index \assign{ptr}
    \begin{itemize}
    \item A better column title is needed.
    \item The formatting should be adaptable.
    \item The index must be sorted.
    \end{itemize}
  \item \Done Mark entries
    \begin{itemize}
    \item Make subsets (lists or sequences) out of marked entreis;
      associate them with a name \dots
    \end{itemize}
 
  \end{itemize}


\subsection{Miscellaneous}
\label{sec:next:misc}

\begin{itemize}
\item A progressbar (rather simple)
\item \Think A check for duplicates. (But this may need a lot of work
  and better fit into a revamped \textit{Import} module.)
\end{itemize}




\subsection{Bugfixes}
\label{sec:next:fix}

\begin{itemize}
\item Stable Working Directory for open.
\end{itemize}
\todoprio{For Release 2.0}

\subsection*{The Graphical User Interface}
\label{todo:r20:gui}

\begin{itemize}
\item Moving to \textsf{GTK 2}.

\end{itemize}


\subsection{Generalities}
\label{todo:r20:genera}

\begin{itemize}
\item Moving to \textsf{Unicode}.
\item Elementary database substructure.
\end{itemize}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "td-td1"
%%% End: 
